%----------------------------------------------------------------------------------------
% HEADER COMMENT
%----------------------------------------------------------------------------------------
% Purpose: LaTeX template for Luong Dang's resume.
%          Generates a PDF resume. Content is defined within this .tex file.
% Key Details: Uses standard article class, common LaTeX packages for formatting.
%              Defines custom commands for resume sections (\resumeSubheading, etc.).
% Related Files: None (Content is hardcoded in this .tex file)
%----------------------------------------------------------------------------------------

\documentclass[letterpaper,10pt]{article}

%----------------------------------------------------------------------------------------
% PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use full page
\usepackage{titlesec} % Allows customization of titles
\usepackage{marvosym} % Required for symbols like phone/email
\usepackage[usenames,dvipsnames]{color} % Allows using color names
\usepackage{verbatim} % Allows environments for comments
\usepackage{enumitem} % Customize lists
\usepackage[hidelinks]{hyperref} % For clickable links (email, linkedin, github)
\usepackage{fancyhdr} % To manage headers/footers (empty here)
\usepackage[english]{babel}
\usepackage{tabularx} % For tables with adjustable column widths
\usepackage{ragged2e} % For \justifying text in About section
\input{glyphtounicode} % Ensure PDF is machine readable/ATS parsable
\pdfgentounicode=1

%----------------------------------------------------------------------------------------
% FONT OPTIONS (Comment out unused ones)
%----------------------------------------------------------------------------------------
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro} % Example: Using Source Sans Pro
% \usepackage{CormorantGaramond}
% \usepackage{charter}

%----------------------------------------------------------------------------------------
% PAGE STYLE & MARGINS
%----------------------------------------------------------------------------------------
\pagestyle{fancy} % Use fancyhdr page style
\fancyhf{} % Clear all header and footer fields
\fancyfoot{} % Clear footer
\renewcommand{\headrulewidth}{0pt} % No header rule
\renewcommand{\footrulewidth}{0pt} % No footer rule

% Adjust margins (tightened further)
\addtolength{\oddsidemargin}{-0.75in} % Was -0.6in
\addtolength{\evensidemargin}{-0.75in} % Was -0.6in
\addtolength{\textwidth}{1.5in} % Was 1.2in
\addtolength{\topmargin}{-.75in} % Was -0.6in
\addtolength{\textheight}{1.5in} % Was 1.2in

\urlstyle{same} % Keep URL style consistent
\raggedbottom % Prevent extra vertical space stretching
\raggedright % Right align text (standard resume format)
\setlength{\tabcolsep}{0in} % Remove padding between table columns

%----------------------------------------------------------------------------------------
% SECTION FORMATTING
%----------------------------------------------------------------------------------------
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large % Format: Small caps, ragged right, large font (vspace adjusted from -6pt)
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}] % Add a horizontal rule under section title (vspace adjusted from -7pt)

%----------------------------------------------------------------------------------------
% CUSTOM COMMANDS -- ADJUSTED SPACING
%----------------------------------------------------------------------------------------
% Command for resume item (bullet point)
\newcommand{\resumeItem}[1]{
  \item\small{ {#1 \vspace{-2pt}} } % Small font, space below (vspace adjusted from -4pt)
}

% Command for subheading (e.g., Job Title, University)
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item % vspace adjusted from -3pt
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-6pt} % Space after subheading (vspace adjusted from -8pt)
}

% Command for project heading
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-3pt}\item % vspace adjusted from -3pt
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \small #2 \\
  \end{tabular*}\vspace{-5pt} % vspace adjusted from -8pt
}

% Command for item lists (like bullet points under a job)
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}} % vspace adjusted from -7pt (Major change for overlap)

% Command for sub-heading lists (groups sections like Education, Experience)
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

% Customize bullet points for nested lists
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

%----------------------------------------------------------------------------------------
% BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

%----------------------------------------------------------------------------------------
% HEADING
%----------------------------------------------------------------------------------------
\begin{center}
    \textbf{\Huge \scshape Luong Dang} \\ \vspace{1pt} % Name
    \small % Contact info
    (510)-541-8379 $|$
    \href{mailto:luongdang0701@gmail.com}{\underline{luongdang0701@gmail.com}} $|$
    \href{https://linkedin.com/in/luong-dang}{\underline{linkedin.com/in/luong-dang}} $|$
    \href{https://github.com/luongkhdang}{\underline{github.com/luongkhdang}}
\end{center}

%----------------------------------------------------------------------------------------
% ABOUT
%----------------------------------------------------------------------------------------
\section{About} 
\small{\justifying % Justify the text in the About section
Full-stack engineer with a builder's drive, proven in fast-paced commercial environments (AAA of SoCal). Experience bootstrapping the technical operations for a growing family business (Kim Tin Jewelry) alongside success in high-responsibility roles. Eager to apply strong technical skills, product intuition sharpened by diverse operational and customer-facing experiences, and a high-impact work ethic to build valuable software solutions and contribute significantly to organizational goals.
} % End \small and \justifying 

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {San Francisco State University}{San Francisco, CA}
      {Bachelor of Science in Computer Science}{GPA: 3.64} % Degree and GPA
    \vspace{1pt} % ADDED: Small positive space to prevent coursework overlap
    \resumeSubheading % Relevant coursework subheading
      {Relevant Coursework}{} % No date/location needed
      {Object-Oriented Programming, Algorithms, Software Design and Implementation, Database Systems, Full-Stack Web Development.}{} % List courses
\resumeSubHeadingListEnd

%----------------------------------------------------------------------------------------
% TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}] % Removed leading spaces
    \small{\item{ % Group skills into categories
        \textbf{Languages}{: Python, TypeScript, JavaScript, SQL, HTML, CSS} \\
        \textbf{Frontend Frameworks/Libraries}{: React, Next.js, React Query, Framer Motion} \\
        \textbf{Backend Frameworks}{: Django, FastAPI, Node.js} \\
        \textbf{Databases}{: PostgreSQL, MySQL, Redis} \\
        \textbf{Cloud \& DevOps}{: REST APIs, JSON, HTTP, AWS, Supabase (PaaS), Docker, Git, Cloudinary (CDN), CI/CD Automation} \\
        \textbf{Concepts}{: OOP, End-to-End Product Development, Retrieval Augmented Generation (RAG), Embeddings, NLP, LLMs (Gemini, LLaMA, Flux.1 AI), Clustering (HDBScan)}
    }}
\end{itemize}

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Experience}
\resumeSubHeadingListStart % Removed leading spaces
    % Job 1
    \resumeSubheading
      {Full-stack Developer / Operations Manager}{Oct 2024 – Present}
      {Kim Tin Jewelry}{Oakland, CA}
      \resumeItemListStart
        \resumeItem{Led the end-to-end technical transformation of a family-owned retail business, significantly improving operational efficiency and enabling strategic growth. Independently designed, developed, and deployed solutions based on stakeholder needs, managing the full development lifecycle.}
        \resumeItem{Built and deployed full-stack automation tools (Python, TypeScript, PostgreSQL) for critical operations (accounting, inventory, CRM), cutting manual workload by 70\%.}
        \resumeItem{Owned the development and shipped custom applications to optimize inventory management and vendor interactions, directly impacting supply chain efficiency.}
        \resumeItem{Launched data-driven digital marketing campaigns using social media and AI (Flux.1) to demonstrably grow the customer base.}
      \resumeItemListEnd

    % Job 2
    \resumeSubheading
      {Insurance Agent (Sales)}{Apr 2022 – Sep 2024}
      {AAA – The Auto Club of Southern California}{Costa Mesa, CA}
      \resumeItemListStart
        \resumeItem{Top 3\% (peaked at \#1 of 255 in Jan-Feb 2024) insurance agent (Personal Lines \& Life) leveraged Computer Science expertise to manage the full sales cycle (lead gen, sales, service, retention) and self-underwrite tailored policies under supervision (avg 100 percent accuracy.)}
        \resumeItem{Transitioning directly from Bachelor's program, collaborated with team members and leadership to provide actionable feedback during Salesforce CRM integration, improving workflow design.}
        \resumeItem{Demonstrated strong problem-solving and initiative by identifying and resolving process inefficiencies, contributing directly to team performance (Team of the Year Regional).}
        \resumeItem{Utilized data analysis and systems thinking (rooted in CS background) to systematically optimize sales processes, analyzed performance data to pinpoint key growth drivers, leading to strategies resulting in Top 3\% national producer ranking (Diamond Club) and multiple performance awards.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}
\resumeSubHeadingListStart % Removed leading spaces
    % Project 1
    \resumeProjectHeading
      {\textbf{NewsReader-Ultimate (Part 2 of Scraper-Ultimate)} $|$ \emph{Python, Google-GenAI, Haystack-RAG, PostgreSQL}}{Apr 2025 – Present}
      \resumeItemListStart
        \resumeItem{Developed a scalable Python pipeline automating news analysis from ingestion to reporting; features include LLM-based preprocessing (summarization, embedding, clustering) and integration with a custom RAG system.}
        \resumeItem{Designed and executed an ETL process: extracted articles from Scraper-Ultimate API, transformed them using local llms and Gemini, and loaded structured results into a PostgreSQL database.}
        \resumeItem{Designed a RAG architecture to retrieve historical articles, entities, and events, enhancing the context and insights of daily reports leveraging Haystack framework. Applied prompt engineering techniques with Google's Gemini 2.5 Pro and its large context window (1 million tokens or 10 small novels) within the RAG pipeline to generate comprehensive daily reports, encompassing recaps, interpretations, patterns, and opinions.}
      \resumeItemListEnd

    % Project 2
    \resumeProjectHeading
      {\textbf{Scraper-Ultimate} $|$ \emph{Python, FastAPI, PostgreSQL, Docker}}{Mar 2025 – Apr 2025}
      \resumeItemListStart
        \resumeItem{Developed a robust web scraping pipeline in Python, utilizing libraries such as Playwright and Scrapling to extract structured data from diverse news sources. Implemented advanced anti-detection techniques, including browser fingerprint randomization, HTTP request customization, and adaptive retry mechanisms, to overcome anti-bot protections. Designed the solution to simulate human interaction patterns, effectively bypassing complex security measures such as CAPTCHAs and dynamic overlays, ensuring high-quality data extraction.}
      \resumeItemListEnd

    % Project 3
    \resumeProjectHeading
      {\textbf{House of Iris} $|$ \emph{Next.js, React, Typescript, TailwindCSS, Supabase Postgres}}{Dec 2024 – Present}
      \resumeItemListStart
        \resumeItem{Built and deployed a full-stack application using Next.js/React/TypeScript, demonstrating proficiency in component architecture, state management, and API integration.}
        \resumeItem{Implemented optimized image delivery by integrating the Cloudinary API for transformations and efficient loading.}
        \resumeItem{Created a CRUD operations using Supabase Postgres, enabling persistent storage and retrieval of user-generated content.}
        \resumeItem{Implemented a functional calendar component with scheduling capabilities, managing React state effectively and utilizing EmailJS to send automated confirmation and reminder emails.}
        \resumeItem{Designed a reward mechanic with Framer Motion, incorporating a Gacha system to gamify the user experience and provide incentives.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%----------------------------------------------------------------------------------------
% END DOCUMENT
%----------------------------------------------------------------------------------------
\end{document}